---
name: Dan Prisk
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BA(Hons)
position: Graduate Student
address: Squamish, BC. Canada.
phone: 778 231 5944
email: dan@prisk.ca
website: http://dan.prisk.ca
twitter: danprisk
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(readxl)
knitr::opts_chunk$set(echo = FALSE)
```

# Education

```{r education}

read.csv("data/education.csv") %>%
  detailed_entries(degree, dates, university, location, details)
```

# Research

## Interests
*Environmental Sociology, Social Movements, Social Theory (broadly continental and critical).*

Understanding the social structures that give rise to, and form the outcomes of, contemporary environmental social movements. What structural factors lead people to care about the environment, engage in environmental movements, and align those movements with decolonial environmental and social justice goals?

## Manuscripts in Progress

```{r manuscripts} 

read.csv("data/manuscripts.csv") %>%
  detailed_entries(authors, ,title, authors ,about)

```

# Positions Held

```{r positions} 

read_excel("data/academic_postions.xls", sheet="roles") %>%
  map_df(rev) %>%
  detailed_entries(institution, location, role, dates)

```

# Scholarships and Awards

```{r awards}

read.csv("data/awards.csv") %>%
  brief_entries(title, date, institution_brief)
```

# Professional History

```{r professional}

read_excel("data/professional_history.xls", sheet = "roles") %>%
  detailed_entries(company, location, role, dates)

```
